--- 
title: "RESQUE Profile"
format: 
  dashboard:
    theme: 
      - lumen
      - custom.scss
    nav-buttons:
      - icon: github
        href: https://github.com/nicebread/RESQUE
---

<!-- See https://spencerschien.info/post/r_for_nonprofits/quarto_template/ -->

```{r setup}
library(RESQUER)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(scales)
library(forcats)
library(wordcloud)
library(knitr)
library(openalexR)
library(tibble)
library(kableExtra)

# TODO: Read all files in folder; let users select the folder via dialog box
  applicant_list <- list()
    #incProgress(1/3, detail = paste("Reading json ", 1, "/3"))
    applicant_list[[1]] <- read_RESQUE(system.file("extdata", "resque_Felix2.json", package="RESQUER"))
    applicant_list[[2]] <- read_RESQUE("/Users/felix/Documents/Github/RESQUE/profile/data/resque_1696782133298.json")
    applicant_list[[3]] <- read_RESQUE("/Users/felix/Documents/Github/RESQUE/profile/data/resque_1697454489129.json")
```

<!-- How to include in package: See https://spencerschien.info/post/r_for_nonprofits/quarto_template/ -->



<!-- Leading content (displayed above all cards) -->

```{r preprocess}

applicant <- applicant_list[[1]]

# Split the research outputs into types, reduce to suitable submissions
pubs <- applicant$indicators %>% filter(type == "Publication", P_Suitable == "Yes")


# clean the dois:
dois <- applicant$indicators$doi
dois <- dois %>% 
  str_replace_all("doi: ", "") %>% 
  str_replace_all(" ", "") %>% 
  str_trim()

applicant$indicators$doi_links <- paste0("https://doi.org/", dois)
applicant$indicators$doi_links_md <- paste0("[", applicant$indicators$doi_links, "](", applicant$indicators$doi_links, ")")

applicant$indicators$title_links_html <- paste0("<a href='", applicant$indicators$doi_links, "'>", applicant$indicators$Title, "</a>")


applicant$indicators$P_TopPaper_Select[is.na(applicant$indicators$P_TopPaper_Select)] <- FALSE

# CRediT preprocessing
#--------------------------------------------------------

credit_tab <- table(applicant$credit$Role, applicant$credit$Degree)

# arrange credit roles by weight (Lead > Support > Equal), summed across works
ct_ordered <- as.data.frame.matrix(credit_tab) %>%
    mutate(
        LeadEqual = Lead + Equal,
        Sum = Lead + Equal + Support + NoRole,
        # normalized weight: All "Lead" (=max) would be 1
        weight = (Lead * 4 + Equal * 3 + Support * 1) / (Sum * 4),
        Role = rownames(.)
    ) %>%
    arrange(-LeadEqual, -Support)

applicant$credit$Role <- factor(applicant$credit$Role, levels = rev(rownames(ct_ordered)))

# The "CRediT involvement" categories
# ---------------------------------------------------------------------
# TODO: Refactor into function

credit_inv <- applicant$indicators %>% select(contains("CRediT"))
roles <- colnames(credit_inv) |> str_replace("P_CRediT_", "") |> unCamel0()
roles[roles == "Writing Review Editing"] <- "Writing: Review & Editing"
roles[roles == "Writing Original Draft"]  <- "Writing: Original draft"

main_roles <- rep("", nrow(credit_inv))
for (i in 1:nrow(credit_inv)) {
  leads <- credit_inv[i, ] == "Lead"
  equals <- credit_inv[i, ] == "Equal"
  main_roles[i] <- paste0(
    ifelse(sum(leads)>0, paste0(
      "<b>Lead:</b> ",
      paste0(roles[leads], collapse=", ")), ""),
    ifelse(sum(equals)>0, paste0(
      "<br><b>Equal:</b> ",
      paste0(roles[equals], collapse=", ")), "")
  )
}

credit_inv$sum_lead <- apply(credit_inv[, 1:14], 1, function(x) sum(x=="Lead"))
credit_inv$sum_equal <- apply(credit_inv[, 1:14], 1, function(x) sum(x=="Equal"))
credit_inv$sum_leadequal <- apply(credit_inv[, 1:14], 1, function(x) sum(x %in% c("Lead", "Equal")))
credit_inv$sum_support <- apply(credit_inv[, 1:14], 1, function(x) sum(x=="Support"))

# define the categories
credit_inv$CRediT_involvement <- factor(rep("Low", nrow(credit_inv)), levels=c("Low", "Medium", "High", "Very High"), ordered=TRUE)
credit_inv$CRediT_involvement[credit_inv$sum_lead >= 3] <- "Very High"
credit_inv$CRediT_involvement[credit_inv$sum_leadequal >= 5] <- "Very High"

credit_inv$CRediT_involvement[credit_inv$sum_lead %in% c(1, 2)] <- "High"
credit_inv$CRediT_involvement[credit_inv$sum_leadequal %in% c(3, 4) & credit_inv$CRediT_involvement != "Very High"] <- "High"

credit_inv$CRediT_involvement[credit_inv$sum_equal %in% c(1, 2) & credit_inv$sum_lead == 0] <- "Medium"
credit_inv$CRediT_involvement[credit_inv$sum_support >= 5 & credit_inv$CRediT_involvement <= "Medium"] <- "Medium"

applicant$indicators$CRediT_involvement <- credit_inv$CRediT_involvement
applicant$indicators$CRediT_involvement_roles <- main_roles

rm(credit_inv, main_roles)


#----------------------------------------------------------------
# Call BIP! API for impact measures
#----------------------------------------------------------------

library(curl)

doi_csv <- paste0(applicant$indicators$dois_normalized, collapse=",") |> URLencode(reserved=TRUE)
req <- curl_fetch_memory(paste0("https://bip-api.imsi.athenarc.gr/paper/scores/batch/", doi_csv))

BIP <- jsonlite::fromJSON(rawToChar(req$content)) 
BIP$pop_class <- factor(BIP$pop_class, levels=paste0("C", 1:5), ordered=TRUE)
BIP$inf_class <- factor(BIP$inf_class, levels=paste0("C", 1:5), ordered=TRUE)
BIP$imp_class <- factor(BIP$imp_class, levels=paste0("C", 1:5), ordered=TRUE)
colnames(BIP)[5] <- "three_year_cc"


#----------------------------------------------------------------
# Retrieve submitted works from OpenAlex
#----------------------------------------------------------------

all_pubs <- applicant$indicators[applicant$indicators$type == "Publication", ]

all_papers <- oa_fetch(entity = "works", doi = all_pubs$doi_links)

#cat(paste0(nrow(all_papers), " out of ", nrow(all_pubs), " submitted publications could be automatically retrieved with openAlex.\n"))

if (nrow(all_papers) < nrow(all_pubs)) {
  warning(paste0(
    '## The following papers could *not* be retrieved by openAlex:\n\n',
    all_pubs[!all_pubs$doi_links %in% all_papers$doi, ] %>%
    select(Title, Year, DOI, P_TypePublication)
  ))
}

all_papers$n_authors <- sapply(all_papers$author, nrow)

all_papers$team_category <- cut(all_papers$n_authors, breaks=c(0, 1, 5, 15, Inf), labels=c("Single authored", "Small team (<= 5 co-authors)", "Large team (6-15 co-authors)", "Big Team (> 15 co-authors)"))

applicant$all_papers <- all_papers
rm(all_papers)

#----------------------------------------------------------------
# Create table of publications
#----------------------------------------------------------------

ref_list <- left_join(applicant$all_papers, applicant$indicators %>% select(doi=doi_links, CRediT_involvement, CRediT_involvement_roles, title_links_html, P_TopPaper_Select), by="doi") %>% 
  arrange(-P_TopPaper_Select, -as.numeric(CRediT_involvement))

names_vec <- c()
for (i in 1:nrow(ref_list)) {
  names_vec <- c(names_vec, format_names(ref_list[i, ], alphabetical = TRUE))
}

ref_table <- data.frame(
  Title=paste0(ifelse(ref_list$P_TopPaper_Select, "â­ï¸", ""), ref_list$title_links_html),
  Authors = names_vec,
  ref_list$CRediT_involvement,
  ref_list$CRediT_involvement_roles
)

colnames(ref_table) <- c("Title", "Authors (alphabetical)", "Candidates' CRediT involvement", "Candidates' CRediT main roles")

applicant$ref_table <- ref_table
rm(ref_table, ref_list)

```


<!-- This document summarizes the research style of `r applicant$meta$FullName` - the *"fingerprint" of how research is conducted*, when only the best work is submitted to this analysis. -->




# Submitted works {orientation="columns"}

## Column1 {width=30%}

### Row {height=45%}
::: {.card title="Type of method"}
```{r types_of_papers}
dat_tM <- applicant$indicators %>% select(contains("P_TypeMethod"))

# add missing columns
expected_columns<- c(
  P_TypeMethod_Empirical = FALSE,
  P_TypeMethod_MetaAnalysis = FALSE, 
  P_TypeMethod_Theoretical = FALSE, 
  P_TypeMethod_Simulation = FALSE,
  P_TypeMethod_OtherMethod = FALSE
)
# adding those columns to df1
dat_tM <- add_column(dat_tM, !!!expected_columns[setdiff(names(expected_columns), names(dat_tM))])

# remove the free text field for this table
dat_tM$P_TypeMethod_Other <- NULL

dat_tM_tab <- pivot_longer(dat_tM, everything()) %>% 
  group_by(name) %>% 
  summarise(paper_count=sum(value, na.rm=TRUE))

dat_tM_tab$name <- str_replace(dat_tM_tab$name, "P_TypeMethod_", "")
dat_tM_tab <- unCamel(df=dat_tM_tab, cname="name")

colnames(dat_tM_tab) <- c("Type of method", "# papers")
kable(dat_tM_tab)
```
:::

### Row {height=55%}
::: {.card title="Journals where the author published"}
::: {style="font-size: 85%;"}
According to [CoARA Commitment 3](https://coara.eu/agreement/the-commitments/), research outputs should neither be assessed based on the journal where it was published, nor on metrics relating to the publication venue. We list the journals where the candidate published to allow a judgement of the field and the relevancy of the author's publication profile for the position. Journals are ordered by frequency and then alphabetically:

```{r journal_list}
#| results: asis
jt <- table(applicant$all_papers$so)
jt2 <- jt[order(jt, names(jt))]
cat(paste0(names(jt2), collapse=", "))
```
:::
:::

## Col2: Ref_table {width=70%}

::: {.card title="Submitted works"}
**Note:**

- Author order has been re-arranged to be alphabetical. Please infer the author's contributions from the CRediT taxonomy.
- Journal names have been removed.
- â­ï¸ = selected as one of the best works.

::: {style="font-size: 80%;"}
```{r}
#| results: "asis"

# Disable Quarto post-processing for this table
# (otherwise column_spec does not work)
kable(applicant$ref_table, format = "html", escape = FALSE, table.attr = "quarto-disable-processing=true") %>% 
  column_spec(1, width = "25%") %>% 
  column_spec(2, width = "25%") %>% 
  column_spec(3, width = "10%") %>% 
  column_spec(4, width = "40%")
```
:::

:::



# Author contributions {orientation="columns"}

## Column1 {width=30%}

::: {.card title="Type of collaboration"}
```{r team_science}
team_tab <- table(applicant$all_papers$team_category) |> as.data.frame()
team_tab$perc <- paste0(round(team_tab$Freq*100 / nrow(applicant$all_papers)), "%")
colnames(team_tab) <- c("Team category", "Frequency", "%")
kable(team_tab, align=c("l", "r", "r"))
```
:::



## Column2 {height=70%}

### Column {.tabset}

```{r credit_barchart, out.width="100%", fig.width = 8, fig.height = 5}
#| title: CRediT Barchart

ggplot(applicant$credit, aes(x = Role, fill = Degree)) +
    geom_bar(stat = "count") +
    coord_flip() +
    scale_fill_manual(values = rev(c("grey90", "indianred1", "khaki2", "green3", "green4")), breaks = rev(c("not applicable", "NoRole", "Support", "Equal", "Lead"))) +
    theme_minimal() + xlab("") + ylab("# of publications") + 
    theme(axis.text.y = element_text(size = 14)) + 
    # force whole integers on x-axis
    scale_y_continuous(breaks = function(x) seq(floor(min(x)), ceiling(max(x)), by = 1))

```

```{r credit_wordcloud}
#| title: CRediT Word Cloud
if (any(ct_ordered$weight > 0)) {
  wordcloud(ct_ordered$Role, freq = ct_ordered$weight, scale = c(2, .1), min.freq = 0.4, random.order = FALSE)  
}
```


### Column

Test



# Impact {orientation="columns"}

## Column1 {width=30%}

### Row1 {height=20%}
```{r}
#| content: valuebox
#| title: "Highly impactful papers:"
#| icon: rocket-takeoff
#| color: primary
list(
  value = sum(BIP$pop_class <= "C4")
)
```

### Row2 {height=80%}
::: {.card title="Research impact: Highly popular publications"}
[BIP! Scholar](https://bip.imsi.athenarc.gr/site/home) (a non-commercial open-source service to facilitate fair researcher assessment) provides impact scores for publications. It provides **five impact classes** based on norm values:

::: {style="font-size: 80%;"}
- Top 0.01%           
- Top 0.1%            
- Top 1%              
- Top 10%             
- Average (Bottom 90%)
:::


Here, we consider the **Popularity** measure. From `r nrow(applicant$indicators)` submitted papers of `r applicant$meta$FullName`, `r nrow(BIP %>% filter(pop_class <= "C4"))` `r ifelse(nrow(BIP %>% filter(pop_class <= "C4")) == 1, "was", "were")` in the top 10% popularity class of all papers or better.

::: {.callout-note title="Computation of the Popularity metric" collapse="true"}
This indicator reflects impact/attention of an article in the research community at large. It is based on *AttRank*, a variation of PageRank (known from the Google search algorithm) that accounts for the temporal evolution of the citation network. By that, it alleviates the bias against younger publications, which have not had the chance to accumulate a lot of citations. It models a researcher's preference to read papers which received a lot of attention recently. It was evaluated (and vetted) in its performance to predict the ranking of papers concerning their *future impact* (i.e., citations). For more details, see [BIP! glossary](https://bip.imsi.athenarc.gr/site/indicators) and the references therein.
:::

:::


## Column2 {width=70%}

::: {.card title="Highly popular papers"}
::: {style="font-size: 80%;"}
```{r}
#| results: "asis"
#| fill: false

pop_sel <- BIP %>% 
  filter(pop_class <= "C4") %>% 
  arrange(pop_class, -three_year_cc) %>% 
  select(doi, three_year_cc, cc,	pop_class)

pop_sel$Label <- factor(pop_sel$pop_class, levels=paste0("C", 1:5), labels=c("Top 0.01%", "Top 0.1%", "Top 1%", "Top 10%", "Average (Bottom 90%)"))
pop_sel$pop_class <- NULL

pop_sel <- left_join(pop_sel, applicant$indicators %>% select(doi=dois_normalized, Title, CRediT_involvement, CRediT_involvement_roles), by="doi") %>% 
  relocate(Title)

colnames(pop_sel) <- c("Title", "doi", "3 year citation count", "Overall citation count", "Popularity", "Candidates' CRediT involvement", "Candidates' CRediT main roles")

pop_sel$doi <- NULL

# add some emojis:
pop_sel$Title[pop_sel$Popularity == "Top 0.01%"] <- paste0("ðŸš€", pop_sel$Title[pop_sel$Popularity == "Top 0.01%"])
pop_sel$Title[pop_sel$Popularity == "Top 0.1%"] <- paste0("ï¸ðŸŒŸ", pop_sel$Title[pop_sel$Popularity == "Top 0.1%"])
pop_sel$Title[pop_sel$Popularity == "Top 1%"] <- paste0("ï¸âœ¨", pop_sel$Title[pop_sel$Popularity == "Top 1%"])

if (nrow(pop_sel) > 0) {
  kable(pop_sel, format = "html", escape = FALSE) %>%
    kable_styling(font_size = 6)
} else {
}
```
:::
:::

# Open Science {orientation="columns"}

## Column1 {width=33%}


::: {.card title="Was the research preregistered / a registered report?"}
```{r}
#| fig-width: 10
#| fig-height: 4

pubs$P_Preregistration2 <- factor(pubs$P_Preregistration, levels=c("NotApplicable", "No", "Yes", "RegisteredReport"), labels=c("Not<br>Applicable", "Not<br>prereg", "Prereg", "Registered<br>Report"))

prereg_tab <- table(pubs$P_Preregistration2) |> as.data.frame() %>%
  mutate(perc = round(Freq*100/sum(Freq)))

# give missing categories a minimal width to make them visible
#prereg_tab$perc[prereg_tab$perc == 0] <- 0.2


BC_h(
  cat_labels=prereg_tab$Var1,
  values=prereg_tab$Freq,
  colors=c("#eeeeee", "#FED976", "#90c916", "#008000"), rev=TRUE)
```
:::


::: {.card title="Preregistered replication attempt"}
```{r}
#| fig-width: 10
#| fig-height: 4

if (!is.null(pubs$P_PreregisteredReplication)) {

pubs$replication <- factor(pubs$P_PreregisteredReplication, levels=c("NotApplicable", "No", "Yes"), labels=c("not<br>applicable", "No", "Yes"))

# fix some logical dependencies
pubs$replication[is.na(pubs$replication) & pubs$P_Preregistration2 == "Not preregistered"] <- "No"

repl_tab <- table(pubs$replication) |> as.data.frame() %>%
  mutate(perc = round(Freq*100/sum(Freq))) %>% 
  filter(perc > 0)

BC_h(
  cat_labels=repl_tab$Var1,
  values=repl_tab$Freq,
  colors=c("#eeeeee", "#FED976", "#90c916"))
}


```
:::


## Column2 {width=33%}

## Column3 {width=33%}
