---
title: "RESQUE Profile for `r params$FullName`"
embed-resources: true
format:
  html:
    unsafe: true
toc: true
params:
  FullName: "Max Mustermann Demoprofile"
  json_path: "/Users/felix/LMU/DGPs Kommission Open Science/RESQUE/Test 0/resque_Leising.json"
---


```{r}
#| include: false

library(knitr)
library(kableExtra)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo=FALSE,
  message=FALSE,
  warning=FALSE,
  out.width="100%"
)

# Set global chunk options for tables
options(knitr.table.format = "html")

# Set default kableExtra styling options
knit_hooks$set(kable = function(x, options) {
  kable(x, format = "html") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
})
```

<style>
table, th, td {
  border: 1px solid #BBBBBB;
  border-collapse: collapse;
}
</style>


```{r}
#| results: "asis"

if (is.null(params$json_path)) {
  cat("\n\n::: {.callout-warning}\nNo data supplied - using demo profile\n:::\n\n")
}
```


```{r setup}
library(RESQUER)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(scales)
library(forcats)
library(wordcloud)
library(knitr)
library(openalexR)
library(tibble)
library(OAmetrics)
library(sparkline)

#params$json_path = "/Users/felix/LMU/DGPs Kommission Open Science/RESQUE/Mainz Test 1/resque_leehr.json"
#params$json_path = "/Users/felix/LMU/DGPs Kommission Open Science/RESQUE/Test 0/resque_Schoenbrodt.json"
# file=system.file("extdata/demo_profiles/resque_Schoenbrodt.json"

if (is.null(params$json_path)) {
  applicant_json <- read_RESQUE(file=system.file("extdata/demo_profiles/resque_Schoenbrodt.json", package="RESQUER"))
} else {
  applicant_json <- read_RESQUE(file=params$json_path)
}

applicant <- preprocess(applicant=applicant_json)

```


# Internationality and Interdisciplinarity

::: {.callout-note title="Methods: Computation of Internationality and Interdisciplinarity" collapse="true"}
The analysis is only based on the submitted publications (not the entire publication list) of the applicant. Publication and co-author data is retrieved from the OpenAlex data base. Note that preprints are not indexed by OpenAlex and therefore do not contribute to this analysis.

- *Internationality* is measured by Pielou's Evenness Index (Pielou 1966) of the country codes of all co-authors. It considers the 10 most frequent country codes.
- *Interdisciplinarity* is measured by the Evenness Index of the fields (as classified by OpenAlex) of the publications. It considers the 6 most frequent fields.

The evenness indexes are normalized to a scale from 0 (no diversity, everything is one category) to 1 (maximum diversity, all categories are equally represented).
:::

```{r}
n_subfields <- min(nrow(applicant$interdisciplinarity$subfields_tab), 6)

internationality_string <- paste0(sum(applicant$internationalization$country_codes_repeated$n), " unique identifiable co-authors:<br><ul><li>", applicant$internationalization$perc_international, "% from ", nrow(applicant$internationalization$country_codes_repeated)-1, " international countries</li><li>", applicant$internationalization$perc_same_country, "% from the same country</li></ul>")

n_countries <- min(nrow(applicant$internationalization$country_codes_repeated), 10)
country_tab <- applicant$internationalization$country_codes_repeated
colnames(country_tab) <- c("Co-authors' Country Code", "# of Co-authors")

subfield_tab <- applicant$interdisciplinarity$subfields_tab[1:n_subfields, ]
colnames(subfield_tab) <- c("Subfield", "# of papers")

interdisciplinarity_string <- paste0(nrow(applicant$interdisciplinarity$primary_fields_tab_reduced), " primary fields: <ul>", paste0(
  "<li>", applicant$interdisciplinarity$primary_fields_tab_reduced$primary_field, " (", applicant$interdisciplinarity$primary_fields_tab_reduced$n, ")</li>", collapse=" "), "</ul>")
```


```{=html}
<div style="display: flex; flex-direction: column; border: 1px solid #BBBBBB;">
    <!-- Row 1 -->
    <div style="display: flex;">
        <div style="flex: 1; border: 1px solid #BBBBBB; padding: 10px; text-align: center"><b>Internationality</b></div>
        <div style="flex: 1; border: 1px solid #BBBBBB; padding: 10px; text-align: center"><b>Interdisciplinarity</b></div>
    </div>
    <!-- Row 2 -->
    <div style="display: flex;">
        <div style="flex: 1; border: 1px solid #BBBBBB; padding: 10px;">`r slider(applicant$internationalization$international_evenness |> round(2), "Only within country co-authors", "Broad coauthor network from many countries")`</div>
        <div style="flex: 1; border: 1px solid #BBBBBB; padding: 10px;">`r slider(applicant$interdisciplinarity$interdisc_evenness |> round(2), "Single discipline", "Many disciplines")`</div>
    </div>
    
        <!-- Row 3 -->
    <div style="display: flex;">
        <div style="flex: 1; border: 1px solid #BBBBBB; padding: 10px;">`r internationality_string`</div>
        <div style="flex: 1; border: 1px solid #BBBBBB; padding: 10px;">`r interdisciplinarity_string`</div>
    </div>
    
    <!-- Row 4 -->
    <div style="display: flex;">
        <div style="flex: 1; border: 1px solid #BBBBBB; padding: 10px;">`r kable(country_tab, format="html", escape = FALSE, table.attr = "class='table table-sm table-striped small' quarto-disable-processing=true")`</div>
        <div style="flex: 1; border: 1px solid #BBBBBB; padding: 10px;">The main subfields are (multiple categories per paper are possible): `r kable(subfield_tab, format="html", escape = FALSE, table.attr = "class='table table-sm table-striped small' quarto-disable-processing=true")`</div>
    </div>

</div>
```





